---
title: "A gentle guide to using the `{targets}` package for analytic pipelines"
subtitle: "Newcastle, UK"
date: "2024/09/03"
author: "Nicholas Tierney"
institute: The Kids Institute, Australia
format: 
  revealjs:
    theme: [blood, extra.scss]
    incremental: true
    slide-number: true
    show-slide-number: all
    footer: "njtierney.github.io/gentle-intro-targets/slides"
editor: visual
execute: 
  echo: false
  warning: false
  cache: true
  freeze: true
---

```{r}
#| label: library
#| include: false
library(tidyverse)
library(knitr)
library(colorspace)
library(naniar)
library(visdat)
library(icons)
```

```{r}
#| label: source-r-files
#| echo: false
#| message: false
#| output: false
lapply(list.files(here::here("R"), full.names = TRUE), source)
```

```{r}
#| label: helpers
#| include: false

icons_fa <- icons::fontawesome
icon_box <- icon_style(icons_fa$solid$`box-open`, fill = "#f0a800")
icon_link <- icon_style(icons_fa$solid$link, fill = "#f0a800")
icon_twitter <- icon_style(icons_fa$brands$twitter, fill = "#f0a800")
icon_github <- icon_style(icons_fa$brands$github, fill = "#f0a800")
icon_plane <- icon_style(icons_fa$solid$`paper-plane`, fill = "#f0a800")


as_table <- function(...) knitr::kable(..., format='html', digits = 3)

theme_set(
  theme_grey(base_size = 16) +
  theme(
    legend.position = "bottom",
    plot.background = element_rect(fill = "transparent"),
    legend.background = element_rect(fill = "transparent")
  )
)

# **ni**ck's **pa**lette
nipa <- list(red = "#c03018",
             orange = "#f0a800",
             green = "#609048",
             purple = "#484878",
             light_purple = "#A3A3BB",
             light_green = "#AFC7A3",
             light_orange = "#F7D37F",
             light_red = "#DF978B",
             pale_purple = "#ECECF1",
             pale_green = "#D7E3D1",
             pale_orange = "#FBE9BF",
             pale_red = "#EFCBC4")

```

# Motivation

-   Data analysis is interactive/messy
-   How to know if it is up-to-date? Better re-run...
-   Months later, how did you do things? Better re-run...
-   Thinking about data analysis deserves inherent structure
-   **You are always collaborating with your future self**
-   {targets} is a way to manage complexity
    -   It's also a mindset, a philosophy.

# I have 3 goals

1.  Convince you {targets} is **worth** learning
2.  Convince you that you **can** use it
3.  For you to feel **more confident** writing functions

## How this will all flow

-   Live coding a data analysis
-   Please ask questions throughout
-   A principle: No tricks!
-   A little simplified
-   "What questions do you have?"

# Data analysis: penguins

-   [palmerpenguins](https://github.com/allisonhorst/palmerpenguins)
-   Sexual dimorphism in penguins: [Ecological Sexual Dimorphism and Environmental Variability within a Community of Antarctic Penguins (Genus Pygoscelis)](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0090081#s2)
-   Let's do something similar, build a logistic regression, predicting sex based on penguin bill dimensions

# `begin_demo()`

# Thanks

-   Will Landau
-   Miles McBain
-   Nick Golding
-   Eric Scott

# Resources

-   https://books.ropensci.org/targets/
-   https://milesmcbain.github.io/ssa_targets_workshop/
-   https://github.com/MilesMcBain/tflow
-   https://github.com/MilesMcBain/fnmate

# Colophon

-   Slides made using [quarto](https://github.com/quarto-dev/quarto)
-   Colours taken + modified from [lorikeet theme from ochRe](https://github.com/ropenscilabs/ochRe) [njtierney/njt-talks](github.com/njtierney/njt-talks) <!-- - Header font is **Josefin Sans** --> <!-- - Body text font is **Montserrat** --> <!-- - Code font is **Fira Mono** --> <!-- - template available:  -->

# Learning more

`r icon_box` [targets](https://books.ropensci.org/targets/)

`r icon_link` [talk link]()

`r icon_github` njtierney

`r icon_plane` nicholas.tierney\@gmail.com

# **End.**
